---
title: "Another Round Experiment II"
author: "Xinwei"
date: "7/31/2020"
output: 
 html_document:
     toc: true
     toc_depth: 3   
     theme: united
     number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
library(CVXR)
library(MASS)
library(R.matlab)
library(e1071)
library(kernlab)
library(glmnet)
library(ggpubr)
library(truncnorm)
library(ggplot2)
rm(list=ls())
setwd("~/Desktop/Multiclass Classification/MSVM Code")
source("primary form functions.R")
source("kernel primary form functions.R")



plot_batch <- function(train_data, test_data, test_data2, C, lambda, intercept = T){
    
  WW_fit <- WW_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept)
  predicted_label <- predict(WW_fit, test_data$X) 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(WW_fit, test_data2$X)== test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("WW:",paste(paste(acc, collapse = ","), paste(acc_g, collapse = ","), sep = "\n"))
  g1.1 <- plot_decision_boundary(WW_fit, print = F, title = title)
  
  CS_fit <- CS_pri_opt(train_data$X,train_data$y,  C=C, lambda=lambda, intercept = intercept)
  predicted_label <- predict(CS_fit, test_data$X) 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(CS_fit, test_data2$X) == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("CS:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g1.2 <- plot_decision_boundary(CS_fit, print = F, title = title)
  
  Duchi_fit <- Duchi_pri_opt(train_data$X,train_data$y,  C= 1, lambda=0, intercept = T)
  predicted_label <- predict(Duchi_fit, test_data$X) 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(Duchi_fit, test_data2$X) == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("Duchi:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g1.3 <- plot_decision_boundary(Duchi_fit, print = F, title = title)
  
  MDuchi_fit <- MDuchi_pri_opt(train_data$X,train_data$y,  C=C, lambda=lambda, intercept = intercept)
  predicted_label <- predict(MDuchi_fit, test_data$X) 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(MDuchi_fit, test_data2$X) == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("MDuchi:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g1.4 <- plot_decision_boundary(MDuchi_fit, print = F, title = title)
  


  
  New1_fit <- New1_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 1)
  predicted_label <- predict(New1_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(New1_fit, test_data2$X, rule = "dagger") == test_data2$y) *100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("New1:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g2.1 <- plot_decision_boundary(New1_fit, print = F, title = title, rule = "dagger") 
  
    
  New1_fit <- New1_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 2)
  predicted_label <- predict(New1_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(New1_fit, test_data2$X, rule = "dagger") == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("New1:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g2.2 <- plot_decision_boundary(New1_fit, print = F, title = title, rule = "dagger") 
  
  New1_fit <- New1_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 3)
  predicted_label <- predict(New1_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(New1_fit, test_data2$X, rule = "dagger") == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("New1:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g2.3 <- plot_decision_boundary(New1_fit, print = F, title = title, rule = "dagger") 
  
    
  New1_fit <- New1_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 4)
  predicted_label <- predict(New1_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(New1_fit, test_data2$X, rule = "dagger")  == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("New1:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g2.4 <- plot_decision_boundary(New1_fit, print = F, title = title, rule = "dagger") 
  
  

  fit <- glmnet(x =  train_data$X, y =  train_data$y, family = "multinomial", lambda=0, intercept = T)
  Multinom_fit <- MDuchi_fit
  Multinom_fit$beta <- t(do.call(cbind,coef(fit)))[,c(2,3,1)]
  predicted_label <- predict(Multinom_fit, test_data$X)
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(Multinom_fit, test_data2$X) == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("Multinom:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g4.4 <- plot_decision_boundary(Multinom_fit, print = F, title = title)


  New3_fit <- New3_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 1)
  predicted_label <- predict(New3_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(New3_fit, test_data2$X, rule = "dagger")  == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("New3:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g3.1 <- plot_decision_boundary(New3_fit, print = F, title = title, rule = "dagger") 
 
  New3_fit <- New3_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 2)
  predicted_label <- predict(New3_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(New3_fit, test_data2$X, rule = "dagger")  == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("New3:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g3.2 <- plot_decision_boundary(New3_fit, print = F, title = title, rule = "dagger") 
  
  New3_fit <- New3_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 3)
  predicted_label <- predict(New3_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(New3_fit, test_data2$X, rule = "dagger")  == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("New3:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g3.3 <- plot_decision_boundary(New3_fit, print = F, title = title, rule = "dagger") 
  
  New3_fit <- New3_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 4)
  predicted_label <- predict(New3_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(New3_fit, test_data2$X, rule = "dagger")  == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("New3:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g3.4 <- plot_decision_boundary(New3_fit, print = F, title = title, rule = "dagger") 
  
  # 
  g4.1 <- tryCatch({
  LLW_fit <- LLW_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept)
  predicted_label <- predict(LLW_fit, test_data$X)
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(LLW_fit, test_data2$X) == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("MSVM7:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  return(plot_decision_boundary(LLW_fit, print = F, title = title, rule = "dagger"))
  }, error = function(e){ NULL})
  
  OVA_fit <- OVA_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept)
  predicted_label <- predict(OVA_fit, test_data$X) 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(OVA_fit, test_data2$X) == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("OVA:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g4.2 <- plot_decision_boundary(OVA_fit, print = F, title = title)
  
  
  
  
  MSVM8_fit <- MSVM8_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept)
  predicted_label <- predict(MSVM8_fit, test_data$X) 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(MSVM8_fit, test_data2$X) == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("MSVM8:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g4.3 <- plot_decision_boundary(MSVM8_fit, print = F, title = title)
  
  
  MSVM7_fit <- MSVM7_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 1)
  predicted_label <- predict(MSVM7_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(MSVM7_fit, test_data2$X, rule = "dagger")  == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("MSVM7:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g5.1 <- plot_decision_boundary(MSVM7_fit, print = F, title = title, rule = "dagger") 
  
  MSVM7_fit <- MSVM7_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 2)
  predicted_label <- predict(MSVM7_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(MSVM7_fit, test_data2$X, rule = "dagger") == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("MSVM7:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g5.2 <- plot_decision_boundary(MSVM7_fit, print = F, title = title, rule = "dagger") 
  
  MSVM7_fit <- MSVM7_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 3)
  predicted_label <- predict(MSVM7_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(MSVM7_fit, test_data2$X, rule = "dagger") == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("MSVM7:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g5.3 <- plot_decision_boundary(MSVM7_fit, print = F, title = title, rule = "dagger") 
    
  MSVM7_fit <- MSVM7_pri_opt(train_data$X,train_data$y, C=C, lambda=lambda, intercept = intercept, base_class = 4)
  predicted_label <- predict(MSVM7_fit, test_data$X, rule = "dagger") 
  acc <- c(round(mean(predicted_label == test_data$y)*100,2),round(mean(predict(MSVM7_fit, test_data2$X, rule = "dagger") == test_data2$y)*100,2))
  acc_g <- round(c(mean(predicted_label[test_data$y == 1]==1), mean(predicted_label[test_data$y == 2]==2), mean(predicted_label[test_data$y == 3]==3))*100,2)
  title <- paste("MSVM7:",paste(paste(acc, collapse = ","),  paste(acc_g, collapse = ","), sep = "\n"))
  g5.4 <- plot_decision_boundary(MSVM7_fit, print = F, title = title, rule = "dagger") 
  
  ggarrange(g1.1, g1.2, g1.3, g1.4,
            g2.1, g2.2, g2.3, g2.4,
            g3.1, g3.2, g3.3, g3.4,
            g4.1, g4.2, g4.3, g4.4,
            g5.1, g5.2, g5.3, g5.4, ncol=4, nrow = 5, common.legend = TRUE, legend="bottom")
  

}

```

# Four-class Gaussian Weakly Separable 2:1

```{r echo=F}

generate_noise_four_gaussian <- function(n, sep = 2, sep_n, train = T){
  
  
  t <- sample(seq(1,4), size = n, replace = T)
  
  dat <- t(sapply(t , function(z){
    if(z==1){
      x <- mvrnorm(1,c(2,0), sep^2*diag(1,2))
    }else if(z==2){
      x <- mvrnorm(1,c(0,2), sep^2*diag(1,2))
    }else if(z==3){
      x <- mvrnorm(1,c(0,-2), sep^2*diag(1,2))
    }else if(z==4){
      x <- mvrnorm(1,c(-2,0) , sep^2*diag(1,2))
    }
    
    
    if(z==1){
      y = sample(seq(1,4), size=1, prob= c(1, 0, 0, 0))
    }else if(z==2){
      y = sample(seq(1,4), size=1, prob= c(0, 1, 0, 0))
    }else if(z==3){
      y = sample(seq(1,4), size=1, prob= c(0, 0, 1, 0))
    }else if(z==4){
      y = sample(seq(1,4), size=1, prob= c(0, 0, 0, 1))
    }
    
    return(c(x,y))
  }))  
  if(train==T){
  N_n <- n/2
  X_n <- mvrnorm(N_n, c(0,0), sep_n^2*diag(1,2))
  y_n <- sample(seq(1,4), size = N_n, replace = T)
  
  X <- dat[,1:2]
  y <- dat[,3]
  
  X <- rbind(X,X_n)
  y <- c(y,y_n)
  t <- c(t,y_n)
  
  }else{
    X <- dat[,1:2]
    y <- dat[,3]
  }
  
  
  list(X=X,y=y, oracle_acc = mean(t==y), t=t)
}


```

## n= 1000
### Sep Noise sigma = 2/3

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
n <- 1000
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/3)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/2

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/2)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/1

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/1)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

## n= 1500
### Sep Noise sigma = 2/3

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
n <- 1500
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/3)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/2

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}

set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/2)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/1

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/1)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

# Four-class Gaussian Weakly Separable 3:2

```{r echo=F}

generate_noise_four_gaussian <- function(n, sep = 2, sep_n, train = T){
  
  
  t <- sample(seq(1,4), size = n, replace = T)
  
  dat <- t(sapply(t , function(z){
    if(z==1){
      x <- mvrnorm(1,c(2,0), sep^2*diag(1,2))
    }else if(z==2){
      x <- mvrnorm(1,c(0,2), sep^2*diag(1,2))
    }else if(z==3){
      x <- mvrnorm(1,c(0,-2), sep^2*diag(1,2))
    }else if(z==4){
      x <- mvrnorm(1,c(-2,0) , sep^2*diag(1,2))
    }
    
    
    if(z==1){
      y = sample(seq(1,4), size=1, prob= c(1, 0, 0, 0))
    }else if(z==2){
      y = sample(seq(1,4), size=1, prob= c(0, 1, 0, 0))
    }else if(z==3){
      y = sample(seq(1,4), size=1, prob= c(0, 0, 1, 0))
    }else if(z==4){
      y = sample(seq(1,4), size=1, prob= c(0, 0, 0, 1))
    }
    
    return(c(x,y))
  }))  
  if(train==T){
  N_n <- floor(n/1.5)
  X_n <- mvrnorm(N_n, c(0,0), sep_n^2*diag(1,2))
  y_n <- sample(seq(1,4), size = N_n, replace = T)
  
  X <- dat[,1:2]
  y <- dat[,3]
  
  X <- rbind(X,X_n)
  y <- c(y,y_n)
  t <- c(t,y_n)
  
  }else{
    X <- dat[,1:2]
    y <- dat[,3]
  }
  
  
  list(X=X,y=y, oracle_acc = mean(t==y), t=t)
}


```

## n= 1000
### Sep Noise sigma = 2/3

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
n <- 1000
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/3)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/2

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/2)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/1

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/1)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

## n= 1500
### Sep Noise sigma = 2/3

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
n <- 1500
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/3)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/2

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}

set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/2)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/1

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/1)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```


# Four-class Gaussian Weakly Separable 1:1

```{r echo=F}

generate_noise_four_gaussian <- function(n, sep = 2, sep_n, train = T){
  
  
  t <- sample(seq(1,4), size = n, replace = T)
  
  dat <- t(sapply(t , function(z){
    if(z==1){
      x <- mvrnorm(1,c(2,0), sep^2*diag(1,2))
    }else if(z==2){
      x <- mvrnorm(1,c(0,2), sep^2*diag(1,2))
    }else if(z==3){
      x <- mvrnorm(1,c(0,-2), sep^2*diag(1,2))
    }else if(z==4){
      x <- mvrnorm(1,c(-2,0) , sep^2*diag(1,2))
    }
    
    
    if(z==1){
      y = sample(seq(1,4), size=1, prob= c(1, 0, 0, 0))
    }else if(z==2){
      y = sample(seq(1,4), size=1, prob= c(0, 1, 0, 0))
    }else if(z==3){
      y = sample(seq(1,4), size=1, prob= c(0, 0, 1, 0))
    }else if(z==4){
      y = sample(seq(1,4), size=1, prob= c(0, 0, 0, 1))
    }
    
    return(c(x,y))
  }))  
  if(train==T){
  N_n <- n/1
  X_n <- mvrnorm(N_n, c(0,0), sep_n^2*diag(1,2))
  y_n <- sample(seq(1,4), size = N_n, replace = T)
  
  X <- dat[,1:2]
  y <- dat[,3]
  
  X <- rbind(X,X_n)
  y <- c(y,y_n)
  t <- c(t,y_n)
  
  }else{
    X <- dat[,1:2]
    y <- dat[,3]
  }
  
  
  list(X=X,y=y, oracle_acc = mean(t==y), t=t)
}


```

## n= 1000
### Sep Noise sigma = 2/3

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
n <- 1000
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/3)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/2

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/2)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/1

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/1)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

## n= 1500
### Sep Noise sigma = 2/3

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
n <- 1500
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/3)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/2

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}

set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/2)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

### Sep Noise sigma = 2/1

```{r echo = F, fig.height=15, fig.width=12, warning = FALSE}
set.seed(134)
sep <-  sqrt(2)/2
train_data <- generate_noise_four_gaussian(n, sep =sep, sep_n = 2/1)
test_data <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=F)
test_data2 <- generate_noise_four_gaussian(20000, sep = sep, sep_n = 1, train=T)

plot_batch(train_data, test_data, test_data2, C=1, lambda = 0)
  
```

